Figure 3-Supplement 2a

### 2018-02-14 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
removing violin and name change for stable_line_ccnd1_exp2

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2a"][[1]])
ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 43,
  units = "mm"
)
```

>>>>

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2a"][[1]])
# ggsave(
#   plot = figure,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 43,
#   units = "mm"
# )
```
